---
format: gfm
---

<!-- README.md is generated from README.qmd. Please edit that file -->

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cIRT: Choice Item Response Theory

<!-- badges: start -->
[![R-CMD-check](https://github.com/tmsalab/cIRT/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/tmsalab/cIRT/actions/workflows/R-CMD-check.yaml)
[![CRAN Version Badge](https://www.r-pkg.org/badges/version/cIRT)](https://cran.r-project.org/package=cIRT)
[![RStudio CRAN Mirror's Monthly Downloads](https://cranlogs.r-pkg.org/badges/cIRT?color=brightgreen)](https://www.r-pkg.org/pkg/cIRT)
[![RStudio CRAN Mirror's Total Downloads](https://cranlogs.r-pkg.org/badges/grand-total/cIRT?color=brightgreen)](https://www.r-pkg.org/pkg/cIRT)
<!-- badges: end -->

Jointly model the accuracy of cognitive responses and item choices
within a Bayesian hierarchical framework as described by Culpepper and
Balamuta (2015).

## Installation

You can install `cIRT` from CRAN using:

```{r}
#| label: cran-installation
#| eval: false
install.packages("cIRT")
```

Or, you can be on the cutting-edge development version on GitHub using:

```{r}
#| label: gh-installation
#| eval: false
if(!requireNamespace("remotes")) install.packages("remotes")
remotes::install_github("tmsalab/cIRT")
```

## Usage

To use the `cIRT` package, load it into _R_ using:

```{r}
#| label: load-package
#| message: false
library("cIRT")
```

## Authors

Steven Andrew Culpepper and James Joseph Balamuta

## Citing the cIRT package

To ensure future development of the package, please cite `cIRT`
package if used during an analysis or simulation studies. Citation information
for the package may be acquired by using in *R*:

```{r}
#| label: citation
#| eval: false
citation("cIRT")
```

## License

GPL (>= 2)
