---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# cIRT: Choice Item Response Theory

<!-- badges: start -->
[![R-CMD-check](https://github.com/tmsalab/cIRT/workflows/R-CMD-check/badge.svg)](https://github.com/tmsalab/cIRT/actions)
[![Package-License](https://img.shields.io/badge/license-GPL%20(%3E=2)-brightgreen.svg?style=flat)](http://www.gnu.org/licenses/gpl-2.0.html)
[![CRAN Version Badge](https://www.r-pkg.org/badges/version/cIRT)](https://cran.r-project.org/package=cIRT)
[![CRAN Status](https://cranchecks.info/badges/worst/cIRT)](https://cran.r-project.org/web/checks/check_results_cIRT.html)
[![RStudio CRAN Mirror's Monthly Downloads](https://cranlogs.r-pkg.org/badges/cIRT?color=brightgreen)](https://www.r-pkg.org/pkg/cIRT)
[![RStudio CRAN Mirror's Total Downloads](https://cranlogs.r-pkg.org/badges/grand-total/cIRT?color=brightgreen)](https://www.r-pkg.org/pkg/cIRT)
<!-- badges: end -->

Jointly model the accuracy of cognitive responses and item choices
within a Bayesian hierarchical framework as described by Culpepper and
Balamuta (2015).

## Installation

You can install `cIRT` from CRAN using:

```{r cran-installation, eval = FALSE}
install.packages("cIRT")
```

Or, you can be on the cutting-edge development version on GitHub using:

```{r gh-installation, eval = FALSE}
if(!requireNamespace("devtools")) install.packages("devtools")
devtools::install_github("tmsalab/cIRT")
```

## Usage

To use the `cIRT` package, load it into _R_ using:

```{r example, message = FALSE}
library("cIRT")
```

## Authors

Steven Andrew Culpepper and James Joseph Balamuta

## Citing the cIRT package

To ensure future development of the package, please cite `cIRT`
package if used during an analysis or simulation studies. Citation information
for the package may be acquired by using in *R*:

```{r, eval = FALSE}
citation("cIRT")
```

## License

GPL (>= 2)
